Notebook

### 2022-03-05 doc/notebook/notebook.Rmd
Change format to html_notebook
Hide code for frog length:weight plot

---
title: "Notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  github_document
---

```{r}
library(tidyverse)
```

@@

```{r, fig.width = 3, fig.align = "center"}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
```

>>>>

---
title: "Notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  html_notebook
---

```{r message=FALSE}
library(tidyverse)
```

@@

```{r frog-lenth-weight-plot, echo=FALSE}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = lm)
plot
```
